---
title: "650projplot"
author: "Shayla Wu"
date: "3/9/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(viridis)
library(hrbrthemes)
library(ggcorrplot)
setwd("~/Desktop/CMM650/650projData")

dt<-read_csv("Data27_edited.csv", col_names = FALSE,skip = 1)
dt <- dt %>% select(-'X2')
```

## tidy data

pivot wider, target-tissue as rows, treatment as cols


```{r,echo=FALSE}
fatdt <- as_tibble(cbind(nms = names(dt), t(dt)))
fatdt<-fatdt[-c(1,2),]
fatdt <- type_convert(fatdt)
fatdt <- fatdt %>% mutate(rowMean=rowMeans(select(fatdt,-c(nms,V2))))
y0dt <- dt[,order(dt[1,])][,c(1:52)]
y1dt <- dt[,order(dt[1,])][,-c(1:52)]
```

## Basic Descriptive Statistics

### Scatter Plot
* No strong corr among chemical treatments (shorter rows) 
* Strong corr among targeted lessions (longer cols)

### Histogram
* row-mean and col-mean concentrate at 8.0-8.1
* Correlation within class Y=0 has range (0.76,0.92), concentrate at [0.8,0.84]
* Correlation within class Y=1 has range (0.8,0.92), concentrate at [0.8,0.84]
* Correlation between classes has range (0.72,0.88)
* No strong linear relationship between two chemical treatments
* Scatter matrix for 3 chemical treatments indicates low corr & different concentate point
* Scatter matrix for 3 target lession indicates no strong difference

```{r, echo=FALSE}
# Histogram of means over each measurement
ggplot(fatdt, aes(x=rowMean, fill = factor(V2))) +
  geom_histogram(position = "identity",
                 alpha = 0.5,
                 bins = 10) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  theme_ipsum()
# Correlation within class Y=0
ggcorr(y0dt[-1,1:10], 
       nbreaks = 50,
       palette = "YlGn",
       drop = TRUE) 
# Try using ggcorrplot, data should be cor matrix
# ggcorrplot(cor(y0dt[-1,1:10]),
#            type="lower",
#            title="Correlations within class Y=0",
#            ggtheme=theme_wsj())
# Correlation within class Y=1
ggcorr(y1dt[-1,1:10], 
       nbreaks = 50,
       palette = "YlGn",
       drop = TRUE) 
# Correlation between classes
x1<-sample(1:52, 5)
x2<-sample(53:288,5)
ggcorr(dt[,order(dt[1,-2])][-1,c(x1,x2)],
       nbreaks = 50,
       palette = "YlGn",
       drop = TRUE) 
# Scatter of two chemical treatments + fitted line
ggplot(fatdt, aes(x = V3, y = V5)) +
  geom_point() +
  stat_smooth(method = lm, level = 0.99) # no strong linear relationship

# Scatter matrix for 3 chemical treatments
ct_scatter<-function(data,mapping){
  ggplot(data=data,mapping=mapping)+
    geom_jitter(alpha=.1,
                color="red")
}
my_density<-function(data,mapping){
   ggplot(data=data,mapping=mapping)+
   geom_density(alpha=.05,
               fill="red")
}
x3 <- sample(3:13213,3)
ggpairs(fatdt[,x3],
        lower=list(continuous=ct_scatter),
        diag=list(continuous=my_density))
# Scatter matrix for 3 target lession
x4 <- sample(3:290,3)
tl_scatter<-function(data,mapping){
  ggplot(data=data,mapping=mapping)+
    geom_jitter(alpha=.05,
                color="grey")
}
ggpairs(dt[-1,x4],
        lower=list(continuous=tl_scatter),
        diag=list(continuous=my_density))
```

```{r}
F1<-read_csv('F1.csv')
F1 <- F1 %>% mutate(PathWay = case_when(...1<=1000~"1",
                                  ...1<=2000~"2",
                                  ...1<=3000~"3",
                                  ...1<=4000~"4",
                                  ...1<=5000~"5",
                                  ...1<=6000~"6",
                                  ...1<=7000~"7",
                                  ...1<=8000~"8",
                                  ...1<=9000~"9",
                                  ...1<=10000~"10",
                                  ...1<=11000~"11",
                                  ...1<=12000~"12",
                                  ...1<=13000~"13"))

F1 %>% group_by(PathWay)%>%
  summarise(count=n(),
            OS=sum(!is.na(Original_Samples)),
            DS=sum(!is.na(Down_Sampling)),
            Dup=sum(Duplication))

F1<-F1 %>% mutate(FeatureCount = case_when(is.na(Original_Samples)~"Down_Sampling",
                                  is.na(Down_Sampling)~"Original_Sample",
                                  TRUE~"Duplications"),
                  is_Original = case_when(is.na(Original_Samples)~"False",
                                    TRUE~"True"),
                  is_DS = case_when(is.na(Duplication)~0,
                                    TRUE~1))
F1<-F1 %>% add_count(PathWay, wt = Duplication)
# Grouped
ggplot(F1, aes(fill=is_Original, x=PathWay)) + 
  geom_bar(alpha=0.7)+
  # scale_fill_viridis(discrete = T) +
  labs(x="Gene PathWay (size=1000)",y="Number of Duplications")+
  ggtitle("Duplications of Important Feature Lists") +
  theme_ipsum()+
  theme(axis.text.x=element_blank()) +
  scale_x_discrete(limits = factor(1:13))

```

